---
title: "Strava Plots"
author: "Sebastian Pahl"
output: html_document
params:
  power: FALSE
  hr: TRUE
  cadence: FALSE
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
library("lubridate")
library("plot3D")
library("plotly")
strava_data <- read.csv("strava_data.csv")
parm_curves <- read.csv("parm_curves.csv")
lubri_time <- as.character(seconds_to_period(strava_data$hours[length(strava_data$hours)]*60*60))
```

:::: {style="display: grid; grid-template-columns: 1.3fr 2fr; grid-column-gap: 10px;"}

::: {}
**Summary Stats**

```
Total time: `r lubri_time`
Total distance: `r round(strava_data$distance[length(strava_data$distance)],2)` km
Total elevation gain: `r sum(pmax(0,strava_data$elevation[-1]-head(strava_data$elevation,-1)))` m
```
:::

::: {}
**Elevation Plot**

```{r, echo=FALSE}
if_parameters <- function() {
        if(params$power) {
                parameters <- list("power", 100, 300, "Power in watts", "watts", "Power Curve", 
                                   "power_zone" ,"Power Zones", "Time in Power Zones", c(0, 150, 200, 300, 400))
        } else if(params$hr) {
                parameters <- list("hr", 110, 160, "Heart rate in bpm", "bpm", "Heart Rate Curve", 
                                   "hr_zone" ,"Heart Rate Zones", "Time in Heart Rate Zones", c(0, 110, 135, 150, 165))
        } else if(params$cadence) {
                parameters <- list("cadence", 70, 90, "Cadence in rpm", "rpm", "Cadence Curve", 
                                   "cadence_zone" ,"Cadence Zones", "Time in Cadence Zones", c(0, 70, 80, 90, 100))
        } 
        names(parameters) <- c("data", "lower", "upper", "label", "units", "curve_title", 
                               "zone_data", "zone_title_1", "zone_title_2", "zones")
        parameters
}
parameters <- if_parameters()

ggplot(data = strava_data) +
geom_point(mapping = aes(x = distance, y = elevation, 
                         colour = pmax(parameters$lower, pmin(parameters$upper, strava_data[,parameters$data]))), 
           size=2) +
scale_x_continuous() +
labs(x = "Distance in km", y = "Elevation in meters", colour = parameters$label) +
scale_colour_gradient(low = "yellow", high = "red", na.value = NA) +
theme(plot.title = element_text(face = "bold", hjust = 0.5))

```
:::

::::

**3D Elevation Plot**\

```{r, echo=FALSE}
scatter3D(x = strava_data$longitude, y = strava_data$latitude, z =strava_data$elevation,
          colvar = pmax(parameters$lower, pmin(parameters$upper, strava_data[,parameters$data])),
          col = ramp.col(c("yellow", "red")),
          theta=-200,  #viewing direction: increasing theta shifts image to the left 
          phi=15,    #viewing direction: increasing phi gives more top view
          bty="g",   #creates an empty perspective box
          type="l",  #or "l" for lines; or "h" for histogram
          lwd=5,
          xlab = "Longitude", ylab = "Latitude", zlab = "Elevation", clab = parameters$label)
```

**Interactive 3D Elevation Plot**\
This only works if you run the .Rmd file in R studio (not by opening the html in a browser)

```{r, echo = FALSE, message=FALSE}
x <- plot_ly(type = "scatter3d",
             data =strava_data, 
             x = ~longitude, y = ~latitude, z = ~elevation, 
             color = pmax(parameters$lower, pmin(parameters$upper, strava_data[,parameters$data])),
             colors = "YlOrRd", size=3)

x <- x %>%  layout(x,scene = list(
        xaxis = list(title = "longitude"),
        yaxis = list(title = "latitude"),
        zaxis = list(title = "elevation"))
)
x
```



:::: {style="display: grid; grid-template-columns: 1.3fr 2fr; grid-column-gap: 10px;"}

::: {}

**Summary Stats**

Peak 1s: `r round(parm_curves[,parameters$data][1])` `r parameters$units`\
Peak 15s: `r round(parm_curves[parm_curves$intervals==15/60,][,parameters$data])` `r parameters$units`\
Peak 1m: `r round(parm_curves[parm_curves$intervals==1,][,parameters$data])` `r parameters$units`\
Peak 5m: `r round(parm_curves[parm_curves$intervals==5,][,parameters$data])` `r parameters$units`\

:::
        
::: {}

**`r parameters$curve_title`**
        
```{r, echo=FALSE}

ggplot(data = parm_curves) +
        geom_line(mapping = aes(x = intervals, y = parm_curves[,parameters$data]), colour = "Red", size = 1.2) +
        labs(x = "Time in Minutes", y = parameters$label)

```
:::

::::



:::: {style="display: grid; grid-template-columns: 1fr 2fr; grid-column-gap: 10px;"}

::: {}

**`r parameters$zone_title_1`**\
\
Zone 1: `r parameters$zones[1]`-`r parameters$zones[2]` `r parameters$units`\
Zone 2: `r parameters$zones[2]`-`r parameters$zones[3]` `r parameters$units`\
Zone 3: `r parameters$zones[3]`-`r parameters$zones[4]` `r parameters$units`\
Zone 4: `r parameters$zones[4]`-`r parameters$zones[5]` `r parameters$units`\
Zone 5: `r parameters$zones[5]`+ `r parameters$units`\

:::
        
::: {}

**`r parameters$zone_title_2`**\
        
```{r, echo = FALSE, message=FALSE}
ggplot(data = strava_data) +
        geom_bar(mapping = aes(x = strava_data[, parameters$zone_data]), stat = "count", 
                 fill = "yellow", colour = "red") +
        labs(x = parameters$zone_title_1, y = "Time in Zone") +
        theme(plot.title = element_text(face = "bold", hjust = 0.5))
```
:::
        
::::

